On the presentation of orthogonal groups over polynomial rings

### 2019-05-07 dl-paper.tex
Added one more assertion

\begin{lemma}
 If $\alpha$ and $\beta$ form a sharp angle then one has $K(\alpha, \beta)^{x_{\beta - \alpha}(a)} \subseteq K(\alpha, \beta)$ for $a \in A$.
\end{lemma}

@@

Full axioms
\begin{enumerate}
 \item $(+)$ $P(\alpha, m)$ contains $\mathrm{K}_2(\Phi, R[t, t^{-1}])$ (or at least the subgroup generated by symbols $\{ X, - \}$ and Steinberg/Dennis--Stein symbols);
 \item $(+)$ if $g \in P(\alpha, m)$ then $S_\alpha(a, g) \cdot h_\alpha^{-1}(1 + am) \in P(\alpha, \frac{m}{1 + am})$;
 %\item if $\alpha \perp \beta$ then $g \in P(\alpha, m) \cap P(\beta, m')$ implies $S_\alpha(a, g) \in P(\beta, m')$;
 \item if $\alpha + \beta \not \in \Phi$ but $\alpha - \beta \in \Phi$, $g \in P(\alpha, m) \cap P(\beta, m')$ then
$S_\alpha(a, g)\cdot  h^{-1}_\alpha(1 + am) \cdot x_{\alpha-\beta}(-N_{\alpha-\beta, \beta}m'a) \in P(\beta, \frac{m'}{1 + am});$
 \item If $\alpha + \beta \in \Phi$ and $g \in P(\alpha, m) \cap P(\alpha + \beta, m')$ then
 $x_\beta(b) \cdot S_\alpha(a, g) \cdot h_{\beta}^{-1}(1+am)\cdot h_{\alpha}^{-1}(1 + N_{\alpha, \beta}abm')\cdot x_{\alpha}(-b(1 + N_{\alpha, \beta}abm')) \in P(\alpha, \frac{m - bm'}{1+am}).$
 \item if $\alpha + \beta \not \in \Phi$ then ???;
\end{enumerate}

Restricted axioms:
\begin{enumerate}
 \item $P(\alpha, 0)$ contains $\mathrm{K}_2(\Phi, R[t, t^{-1}])$ (or at least the subgroup generated by symbols $\{ X, - \}$ and Steinberg/Dennis--Stein symbols);
 \item if $g \in P(\alpha, 0)$ then $S_\alpha(a, g) \in P_\alpha(\alpha, 0)$;
% \item if $\alpha \perp \beta$ then $g \in P(\alpha, 0) \cap P(\beta, 0)$ implies $S_\alpha(a, g) \in P(\beta, 0)$;
 \item if $\alpha + \beta \not \in \Phi$ but $\alpha - \beta \in \Phi$, $g \in P(\alpha, 0) \cap P(\beta, 0)$ then
$S_\alpha(a, g) \in P(\beta, 0);$
 \item If $\alpha + \beta \in \Phi$ and $g \in P(\alpha, 0) \cap P(\alpha + \beta, 0)$ then
 $x_\beta(b) \cdot S_\alpha(a, g) x_{\beta}(-b)\in P(\alpha, 0).$
 \item if $\alpha + \beta \not \in \Phi$ then ???;
\end{enumerate}

>>>>

\begin{lemma} Suppose $\alpha$ and $\beta$ form a sharp angle, then $g \in K(A[X], M[X])$ then 
\[S_\alpha(a, g)\cdot  h^{-1}_\alpha(1 + am) \cdot x_{\alpha-\beta}(-N_{\alpha,-\beta}\cdot m'a) \in P\left(\beta, \frac{m'}{1 + am}\right).\] \end{lemma}
\begin{proof}
 By~\cref{K-a-b} $g = g_0 \cdot x_{-\alpha}(mX) \cdot x_{-\beta}(m'X)$ for some $g_0\in K(\alpha, \beta)$.
 \begin{multline} \nonumber S_\alpha(a, g) = S_\alpha(a, g_0) \cdot S(a, x_{-\alpha}(mX)) \cdot S_\alpha\left(\frac{a}{1+am}, x_{-\beta}(m'X)\right) = \\ = S_\alpha(a, g_0) \cdot \langle -a, m \rangle \cdot h_\alpha(1+am) \cdot x_{-\beta}(m'X) \cdot x_{\alpha-\beta}\left(\frac{N_{\alpha, -\beta} \cdot m'a}{1+am}\right) = \\ =
  S_\alpha(a, g_0) \cdot \langle -a, m \rangle \cdot  x_{-\beta}\left(\frac{m'X}{1+am}\right) \cdot x_{\alpha-\beta}\left(N_{\alpha, -\beta} \cdot m'a\right) \cdot h_\alpha(1+am). \end{multline}
The assertion now follows from the preceding corollary.
\end{proof}

\begin{lemma}
 If $\alpha$ and $\beta$ form a sharp angle then one has $K(\alpha, \beta)^{x_{\beta - \alpha}(a)} \subseteq P_\alpha(0)$ for $a \in A$.
\end{lemma}
\begin{proof}
 It is clear that $K(\alpha, \beta)^{x_{\beta - \alpha}(a)} \subseteq K(A[X], M[X]) \subseteq P_\alpha(*)$.
\end{proof}

@@

Full axioms
\begin{enumerate}
 \item (+) $P(\alpha, m)$ contains $\mathrm{K}_2(\Phi, R[t, t^{-1}])$ (or at least the subgroup generated by symbols $\{ X, - \}$ and Steinberg/Dennis--Stein symbols);
 \item (+) if $g \in P(\alpha, m)$ then $S_\alpha(a, g) \cdot h_\alpha^{-1}(1 + am) \in P(\alpha, \frac{m}{1 + am})$;
 %\item if $\alpha \perp \beta$ then $g \in P(\alpha, m) \cap P(\beta, m')$ implies $S_\alpha(a, g) \in P(\beta, m')$;
 \item (+) if $\alpha + \beta \not \in \Phi$ but $\alpha - \beta \in \Phi$, $g \in P(\alpha, m) \cap P(\beta, m')$ then $S_\alpha(a, g)\cdot  h^{-1}_\alpha(1 + am) \cdot x_{\alpha-\beta}(-N_{\alpha-\beta, \beta}m'a) \in P(\beta, \frac{m'}{1 + am});$
 \item If $\alpha + \beta \in \Phi$ and $g \in P(\alpha, m) \cap P(\alpha + \beta, m')$ then
 $x_\beta(b) \cdot S_\alpha(a, g) \cdot h_{\beta}^{-1}(1+am)\cdot h_{\alpha}^{-1}(1 + N_{\alpha, \beta}abm')\cdot x_{\alpha}(-b(1 + N_{\alpha, \beta}abm')) \in P(\alpha, \frac{m - bm'}{1+am}).$
 \item if $\alpha + \beta \not \in \Phi$ then ???;
\end{enumerate}

Restricted axioms:
\begin{enumerate}
 \item (+) $P(\alpha, 0)$ contains $\mathrm{K}_2(\Phi, R[t, t^{-1}])$ (or at least the subgroup generated by symbols $\{ X, - \}$ and Steinberg/Dennis--Stein symbols);
 \item (+) if $g \in P(\alpha, 0)$ then $S_\alpha(a, g) \in P_\alpha(\alpha, 0)$;
% \item if $\alpha \perp \beta$ then $g \in P(\alpha, 0) \cap P(\beta, 0)$ implies $S_\alpha(a, g) \in P(\beta, 0)$;
 \item (+) if $\alpha + \beta \not \in \Phi$ but $\alpha - \beta \in \Phi$, $g \in P(\alpha, 0) \cap P(\beta, 0)$ then
$S_\alpha(a, g) \in P(\beta, 0);$
 \item If $\alpha + \beta \in \Phi$ and $g \in P(\alpha, 0) \cap P(\alpha + \beta, 0)$ then
 $x_\beta(b) \cdot S_\alpha(a, g) x_{\beta}(-b)\in P(\alpha, 0).$
 \item if $\alpha + \beta \not \in \Phi$ then ???;
\end{enumerate}
